\documentclass{article}
\usepackage{hyperref}
\usepackage{geometry}
\geometry{a4paper, margin=1in}
\usepackage{enumitem}
\setlist[itemize]{leftmargin=*}

\begin{document}

\begin{center}
    \Large\textbf{Aadya Chinubhai} \\
    \normalsize Computer Science Graduate \\
    \normalsize Ahmedabad University
\end{center}

\section*{Contact}
\begin{itemize}
    \item \textbf{GitHub:} \href{https://github.com/aadya940}{aadya940}
    \item \textbf{Email:} [Your Email Address] % Placeholder for actual email
\end{itemize}

\section*{Summary}
A motivated Computer Science graduate from Ahmedabad University with a strong interest in Mathematics, Programming, and building impactful toolchains and libraries. Proficient in Python and C, with solid Computer Science fundamentals. Successfully completed the Google Summer of Code program with NumFOCUS. Actively contributing to open-source projects, including maintaining \href{https://github.com/aeon-toolkit}{aeon-toolkit}. Demonstrates a proactive approach to development and collaboration.

\section*{Skills}
\begin{itemize}
    \item \textbf{Programming Languages:} Python, C
    \item \textbf{Key Interests:} Mathematics, Programming, Toolchains, Libraries, Data Analysis
\end{itemize}

\section*{Projects}
\begin{itemize}
    \item \textbf{chainopy:} A Python Library for Discrete Time Markov Chain based stochastic analysis. (Stars: 17)
    \item \textbf{chaintools:} An implementation of Markov Chains in C with Python Bindings. (Stars: 2)
    \item \textbf{numpyai:} A complete natural language data analysis toolkit using NumPy and LLMs. (Stars: 15)
    \item \textbf{gemma\_demo:} A Chat Interface and Library demonstrating the capabilities of Google's Gemma Models. (Stars: 1)
\end{itemize}

\section*{Open Source Contributions}
\begin{itemize}
    \item Active contributor across various projects, with significant activity noted in months such as March, July, and August.
    \item Specific contribution: Reviewed 1 pull request in \texttt{aeon-toolkit/aeon}, specifically "[GOV] Use the NumFOCUS code of conduct and rename `aeon` workgroup" on June 5th.
\end{itemize}

\section*{Achievements}
\begin{itemize}
    \item Ex-Google Summer of Code @ NumFOCUS
    \item GitHub Achievements: Starstruck (x2), Pull Shark (x2), Pair Extraordinaire.
\end{itemize}

\end{document}